### 2018-07-30 VV570/HW9/submission.tex
question 1 done

\section{Question 1}
	\begin{enumerate}[(a)]
		\item
			It's convex as $f''(x) = e^x > 0$.
		\item 
			Let
			\begin{equation}
				RHS \triangleq t f(x) + (1-t)f(y)
			\end{equation}
			\begin{equation}
				LHS \triangleq - f(tx+(1-t)y)
			\end{equation}
			It's concave as
			\begin{equation}
				\begin{aligned}
				  & RHS-LHS\\
						   = &[t x_1 x_2 + (1-t)y_1 y_2] -[t x_1 + (1-t)y_1][t x_2 + (1-t)y_2]\\
						   = &-t(1-t)(x_1 y_2 + x_2 y_1) < 0
				\end{aligned}
			\end{equation}
		\item 
			Convex.

		\item 
			Convex.

		\item 
			Convex.

		\item 
			Concave.

@@

\section{Question 2}
	\begin{enumerate}[(a)]
		\item 
			\begin{proof}
				Suppose $x = (x_1, x_2, ... , x_m)$, then it's left to prove that
				\begin{equation}
					\frac{\partial f}{\partial x_i} = 0
				\end{equation}
				for $i=1,2, ... , m$ at $x=x^*$.
			\end{proof}
			The partial derivative of $f$ at $x=x^*$ is defined as
			\begin{equation}
				\frac{\partial f}{\partial x_i}\Big|_{x=x^*} = 
				\lim\limits_{\Delta x_i \rightarrow 0}\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i}
			\end{equation}
			Since $f(x^*)$ is the local minimum, $f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) \geq f(x_1, x_2, ... ,x_i^*, ... , x_m)$ however $\Delta x_i$ changes.\\
			Thus
			\begin{equation}
				\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i} \leq 0
			\end{equation} 
			if $\Delta x_i < 0$.\\
			And
			\begin{equation}
				\frac{f(x_1, x_2, ... ,x_i^* + \Delta x_i, ... , x_m) - f(x_1, x_2, ... ,x_i^*, ... , x_m)}{\Delta x_i} \geq 0
			\end{equation}  
			if $\Delta x_i > 0$.\\
			Hence, $\frac{\partial f}{\partial x_i}\Big|_{x=x^*} = 0$ as $f$ is continuously differentiable.
			Therefore, $\triangledown f(x^*) =0$.
		\item 
			\begin{proof}
				With taylor expansion of $f(x)$ at $x=x^*$
				\begin{equation}
					\begin{aligned}
						  &f(x) - f(x^*) \geq 0 \quad \quad (\text{$f(x^*)$ is the local minimum})\\
		  \Leftrightarrow &\triangledown f(x^*) \Delta x + \frac{1}{2} \Delta \xi H(x^*) \Delta \xi ^T \geq 0\\
		  \Leftrightarrow &\frac{1}{2} \Delta \xi H(x^*) \Delta \xi ^T \geq 0 \quad \quad (\text{gradient be 0})
					\end{aligned}
				\end{equation}
				where $d(\Delta \xi, x^*) \leq d(x, x^*)$, and the gradient is $0$ as been proved above.
				Thus, $ \Delta \xi H(x^*) \Delta \xi ^T \geq 0$ for any $\Delta \xi$ within the local neighbourhood of $x=x^*$.\\
				Hence $H(x^*)$ is semi-positive finite.

			\end{proof}
		\item 
			\begin{proof}
				($\Leftarrow$)The global minimum must be a local minimum, and the gradient is therefore 0 as $f$ is differentiable.

				($\Rightarrow$)As has been proved above, $\triangledown f(x^*)=0$ indicates that $f(x^*)$ is the local minimum. It's left to prove that local minimum is also global minimum for a convex function.
				Suppose there exist $x'$ s.t. 
				\begin{equation}
					f(x') < f(x^*)
				\end{equation}
				Then, by convexity
				\begin{equation}
					f(t x' + (1-t)x^*) \leq t f(x') + (1-t) f(x^*) < \leq t f(x^*) + (1-t) f(x^*) = f(x^*)
				\end{equation}
				When $t\rightarrow1$, the inequality above contradicts local optimality of $x^*$.\\
				Thus, the assumption fails, which indicates that $f(x^*)$ is the global minimum for $f$.

			\end{proof}
		\item
			\begin{proof}
				($\Rightarrow$)By Taylor expansion
				\begin{equation}
					f(x+ d) = f(x) + \triangledown f(x) d + \frac{1}{2} d^T H(x) d + O(||d||^2)
				\end{equation}
				If the Hessian matrix $H$ is semi-definite positive, then
				\begin{equation}
					d^T H(x) d \geq 0
				\end{equation}
				Thus
				\begin{equation}
					f(x+ d) \geq f(x) + \triangledown f(x) d
				\end{equation}
				which is the so called 1-st order condition, and it implies that the function $f$ is convex.

				($\Leftarrow$)By Taylor expansion
				\begin{equation}
					f(x+ t d) = f(x) + t \triangledown f(x) d + \frac{t^2}{2} d^T H(x) d + O(||d||^2)
				\end{equation}
				With the 1-st order condition
				\begin{equation}
					f(x+ t d) \geq f(x) + t \triangledown f(x) d
				\end{equation}
				Thus
				\begin{equation}
					\frac{t^2}{2} d^T H(x) d + O(t||d||^2) \geq 0
				\end{equation}
				Dividing it by $\frac{t^2}{2}$ and set $t \rightarrow 0$, it gives out that for any $d\in \mathbb{R}^n$, $d^T H(x) d \geq 0$.

			\end{proof}

\section{Question 4}
	The genetic algorithm is adopted as there exists intensive oscillation when $x$ approaches $0$, and optimization algorithms dependent on the gradient info are easy to fall into local minimum.\\
	The global minimum found is $x_0=0.217, f(x_0)=-0.0249$.

\section{Question 6}
	The plot of $g(y)$ is given as follows
	\begin{figure}[!htbp]
		\centering
		\includegraphics[width=15cm]{../pic/Task6.eps}
	\end{figure}

\section{Question 7}
	According to the geometric relations, the allowable length of the ladder is given as
	\begin{equation}
		L(\alpha) = \min\limits_{\beta} (\frac{1}{sin(\beta)} + \frac{1}{sin(\alpha + \beta)})
	\end{equation}
	By solving the minimisation problem, the plot of $L$ versus $\alpha$ is given as follows
	\begin{figure}[!htbp]
		\centering
		\includegraphics[width=15cm]{../pic/Task7.eps}	
	\end{figure}

>>>>

\section{Question 1}
	\begin{enumerate}[(a)]
		\item
			\begin{proof}
				As $\mathcal{A}$ is convex, the mean value theorem can be applied in terms of $y$ s.t.
				\begin{equation}
					\Phi(t, y_2) - \Phi(t, y_1) = (y_2 - y_1) \frac{\partial \Phi(t, y)}{\partial y}\Big|_{y=\xi} 
				\end{equation}
				where $\xi \in (y_1, y_2)$.\\
				Since the there exists $c>0$ s.t. for all $(t, y)\in \mathcal{A}$
				\begin{equation}
					\Big| \frac{\partial \Phi(t, y)}{\partial y} \Big| \leq c
				\end{equation}
				Thus
				\begin{equation}
					\begin{aligned}
						& |\Phi(t, y_2) - \Phi(t, y_1)|\\
					  = & |y_2 - y_1| \Bigg| \frac{\partial \Phi(t, y)}{\partial y}\Big|_{y=\xi} \Bigg|\\
				   \leq & c |y_2 - y_1|	
					\end{aligned}
				\end{equation}
				which implies that $\Phi(t, y)$ satisfies Lipschitz condition in $y$ on $\mathcal{A}$.
			\end{proof}

		\item 
			\begin{proof}
				Let $P_1 = (t_1, y_1)$ and $P_2 = (t_2, y_2)$. Then any point $P'$ lies on the line segment joining $P_1$ and $P_2$ can be expressed as
				\begin{equation}
					\begin{aligned}
						P & = (1-\alpha)P_1 + \alpha P_2\\
						  & = ((1-\alpha)t_1 + \alpha t_2, (1-\alpha)y_1 + \alpha y_2)\\
						  & \triangleq (t', y')
					\end{aligned}
				\end{equation} 
				where $\alpha \in [0, 1]$.\\
				It's clear that $t_1$ and $t_2$ lies between $t_0$ and $T$, and $t'$ lies between $t_1$ and $t_2$. Thus, $t'$ also lies between $t_0$ and $T$.\\
				Further, it's also clear that $-\infty < y' < +\infty$.\\
				Hence $P \in \mathcal{D}$, which implies that $\mathcal{D}$ is convex.
			\end{proof}

		\item
			\begin{proof}
				Let
				\begin{equation}
					\Phi(t, y) = \frac{4t^3y}{1+t^4}
				\end{equation}
				Then
				\begin{equation}
					\frac{\partial \Phi(t, y)}{\partial y} = \frac{4t^3}{1+t^4} =\frac{4 t}{t^2 + \frac{1}{t^2}} < \frac{4}{t^2 + \frac{1}{t^2}} < \frac{4}{2 \sqrt{t^2 \frac{1}{t^2}}} = 2
				\end{equation}
				as $t\in (0,1)$.\\ 
				which implies that $\Phi(t, y)$ satisfies a Lipschitz condition in $y$.\\
				Thus, the given IVP problem has a unique solution.
			\end{proof}

		\item 
			Definitely not recommended.\\
			As $\Phi(t, y) = 1 + y^2$, then
			\begin{equation}
				\frac{\partial \Phi}{\partial y} = 2 y \triangleq \lambda y
			\end{equation}
			Here $\lambda > 0$, and the Euler's method is not stable as the error will be amplified at each iteration step. Finally the calculation will diverge.
	\end{enumerate}

\section{Question 2}
	\begin{enumerate}[(a)]
		\item

@@

\section{Question 4}

\section{Question 6}
